Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
RW: minors

In our approach, the application partitioning into components is manually specified through a \ac{dsl}.
%
Therefore, it can be framed in the context of \emph{component-based software engineering},
 with ~\cite{vale2016component-based-se} providing a comprehensive review.
%
The specification or design of distributed systems
 may leverage
 component models~\cite{DBLP:journals/tse/CrnkovicSVC11},
 architectural description languages~\cite{DBLP:journals/tse/MedvidovicT00},
 service-based compositions~\cite{DBLP:journals/csur/LemosDB16}, 
 or frameworks.
%
Specifically,
 this work builds on the \emph{pulverisation} component model~\cite{FI2020-pulverization,IEEE-IoTJ-pulverization-simulation}.
 whereby a large-scale cyber-physical system
 is partitioned into a graph of devices
 where each device is split into five deployable components:
 (i) sensors interface,
 (ii) actuators interface,
 (iii) behaviour,
 (iv) state, and
 (v) communication component.
%
In~\cite{IEEE-IoTJ-pulverization-simulation},
 a methodology on top of the pulverisation model
 is proposed
 for generating and testing deployments through simulation.
%
There, file descriptors and scripts are used to generate deployment plans; in \ourframework{}, instead, we provide \acp{dsl} supporting a specification-oriented, declarative approach.
%

@@

In this work,
 we are especially interested in deployments over large-scale cyber-physical systems and the edge-cloud continuum.
%
\emph{MuScADeL}~\cite{DBLP:conf/compsac/BoujbelRLTAL14/muscadel}
 is a \ac{dsl} that allows to express deployment properties of 
applications on multi-scale deployment domains,
i.e., large and heterogeneous infrastructures considered under several viewpoints
(device, geography, network, administrative domains, etc.).
%
In~\cite{DBLP:journals/sosym/SongDFSF22},
  a model-based deployment approach is proposed
  targeting so-called \emph{fleets}, i.e.,
  distributed and heterogeneous devices at the edge characterised by different cyber-physical contexts
(cf. resources, connectivity, etc.).
%
It is based on the \emph{GeneSIS} modelling language,
where a \texttt{DeploymentModel} consists of sets of \texttt{Resources} (e.g., \texttt{Component}s, specialised by \texttt{InfrastructureComponent}s and \texttt{SoftwareComponent}s) with associated \texttt{Property}s and \texttt{Link}s.

>>>>

In our approach, the application partitioning into components is manually specified through a \ac{dsl}.
%
Therefore, it can be framed in the context of \emph{component-based software engineering},
 with ~\cite{vale2016component-based-se} providing a comprehensive review.
%
The specification or design of distributed systems
 may leverage
 component models~\cite{DBLP:journals/tse/CrnkovicSVC11},
 architectural description languages~\cite{DBLP:journals/tse/MedvidovicT00},
 service-based compositions~\cite{DBLP:journals/csur/LemosDB16}, 
 or frameworks.

Specifically,
 this work builds on the \emph{pulverisation} component model~\cite{FI2020-pulverization,IEEE-IoTJ-pulverization-simulation}.
 whereby a large-scale cyber-physical system
 is partitioned into a graph of devices
 where each device is split into five deployable components:
 (i) sensors interface,
 (ii) actuators interface,
 (iii) behaviour,
 (iv) state, and
 (v) communication component.
%
In~\cite{IEEE-IoTJ-pulverization-simulation},
 a methodology on top of the pulverisation model
 is proposed
 for generating and testing deployments through simulation.
%
There, file descriptors and scripts are used to generate deployment plans; in \ourframework{}, instead, we provide \acp{dsl} supporting a specification-oriented, declarative approach.
%

@@

In this work,
 we are especially interested in deployments over large-scale cyber-physical systems and the edge-cloud continuum.
%
\emph{MuScADeL}~\cite{DBLP:conf/compsac/BoujbelRLTAL14/muscadel}
 is a \ac{dsl} that allows to express deployment properties of 
applications on multi-scale deployment domains,
i.e., large and heterogeneous infrastructures considered under several viewpoints
(device, geography, network, administrative domains, etc.).
%
In~\cite{DBLP:journals/sosym/SongDFSF22},
  a model-based deployment approach is proposed
  targeting so-called \emph{fleets}, i.e.,
  distributed and heterogeneous devices at the edge characterised by different cyber-physical contexts
(cf. resources, connectivity, etc.).
%
The main goal is to support the distribution of \emph{multiple variants} of the same application based on the different contexts of the different target devices.
%
The approach based on the \emph{GeneSIS} modelling language,
where a \texttt{DeploymentModel} consists of sets of \texttt{Resources} (e.g., \texttt{Component}s, specialised by \texttt{InfrastructureComponent}s and \texttt{SoftwareComponent}s) with associated \texttt{Property}s and \texttt{Link}s.
